### 2017-05-11 sheets/basis-2/sheet-basis-2.tex
small stilistic change.

  \begin{enumerate}
  \item $\mathbf {Rel}^{\op}\cong \mathbf {Rel}$;
  \item $\mathbf {Set}^{\op}\cong \mathbf {Set}$;
  \item for an arbitrary monoid interpreted as a category $\M$ with one object:  $\M^{\op}\cong \M$; \textit{(Not entirely trivial 1)}
  \item for $\mathbf{CAT_i}$, the subcategory of $\mathbf{CAT}$ consisting of all categories and functors that are isomorphisms: $\mathbf{CAT_i}^{op}\cong\mathbf{CAT_i}$.
  \end{enumerate}

@@

\begin{exercise}[\textit{Not entirely trivial 2}]
  Let $\A$ be a category. Construct a functor $F\from \A\to\mathbf{Cat}$ such that $F(A)=\A/A$ and show that this is indeed a functor. Is this also an isomorphism?

>>>>

  \begin{enumerate}
  \item $\mathbf {Rel}^{\op}\cong \mathbf {Rel}$;
  \item $\mathbf {Set}^{\op}\cong \mathbf {Set}$;
  \item for an arbitrary monoid interpreted as a category $\M$ with one object:  $\M^{\op}\cong \M$; \textit{(Challenge 1)}
  \item for $\mathbf{CAT_i}$, the subcategory of $\mathbf{CAT}$ consisting of all categories and functors that are isomorphisms: $\mathbf{CAT_i}^{op}\cong\mathbf{CAT_i}$.
  \end{enumerate}

@@

\begin{exercise}[\textit{Challenge 2}]
  Let $\A$ be a category. Construct a functor $F\from \A\to\mathbf{Cat}$ such that $F(A)=\A/A$ and show that this is indeed a functor. Is this also an isomorphism?
